More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
a small text for explaining transitivity rule ... not final

\begin{definition}[Operational semantics of open pNets]
	\label{def:operationalSemantics}
	The semantics of a pNet $p$ is an open automaton $A = <Leaves(p),J,\mathcal{S}, s_0,
	\mathcal{T}>$ where:
	\begin{itemize}
		\item $J$ is the set of holes: $Holes(p)= J$. \RAB{Holes(p)= J en ref a 
		page 4}
		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
		\item $\mathcal{T}$ is the smallest set of open transitions
		satisfying the rules below:
	\end{itemize}

@@

       \section{Proofs of basic properties on pNets}
       \subsection{Equivalence relation (Theorem~\ref{thm-equiv})}
        \emph{Suppose $\mathcal{R}$ 
       	is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, 
       	$\mathcal{R}$ is 
       	reflexive, symmetric and transitive.
       	}

@@

>>>>

\begin{definition}[Operational semantics of open pNets]
	\label{def:operationalSemantics}
	The semantics of a pNet $p$ is an open automaton $A = <Leaves(p),J,\mathcal{S}, s_0,
	\mathcal{T}>$ where:
	\begin{itemize}
		\item $J$ is the set of holes: $Holes(p)= J$. 
		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
		\item $\mathcal{T}$ is the smallest set of open transitions
		satisfying the rules below:
	\end{itemize}

@@

       \section{Proofs of basic properties on pNets}
       \subsection{Equivalence relation (Theorem~\ref{thm-equiv})}
        \emph{Suppose $\mathcal{R}$ 
       	is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, 
       	$\mathcal{R}$ is 
       	reflexive, symmetric and transitive.
       	}
%%% A PROOF WITH CONSTRUCTIVE AERGUMENTS BUT THAT DOES NOT WORK

@@

This relation is the adaptation of the transitivity to the conditional relationship that 
defines a bisimulation. Indeed the global disjunction together with the conjuction of 
predicates plays exactly the role of the intermediate element in a transitivity rule: 
``there exists an intermediate state'' corresponds to the global disjunction, and the 
conjunction of states expresses the intermediate predicate is used to ensure 
satisfiability of the predicate relating the first state to the last one..
